Reassessing the Impact of Dynamic Slicing in SFL

### 2018-11-12 paper/main.tex
adding (empty) implementation section
pass on intro

%% Title information
\title{The Impact of Critical Slicing in SFL\Comment{tatistical Fault Localization}}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% PROBLEM MOTIVATION
Automated debugging is very important.\Fix{...elaborate...}

Spectrum-Based Fault Localization (\sfl{}) and Dynamic Slicing are
popular complementary approaches proposed to automate debugging.
\sfl{}~\cite{7390282} is a statistical debugging method that computes
suspiciousness values associated with program entities (e.g., basic
blocks) using coverage information of passing and failing test
cases. \sfl{} produces a list of program entities ranked in
decreasing order of suspiciousness.  \sfl{} received tremendous
attention over the years, but its applicability to support debugging
remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been shown
useful in supporting downstream analyses, such as Automated Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for likely fixes to
likely buggy statements.  Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes. Dynamic Slicing~\cite{Agrawal:1990:DPS:93542.93576} is another popular
technique for automated debugging. It takes as input a failing test
and produces on output a set of statements--the slice--that influence
the evaluation of the fault-revealing assertion.

@@

This paper reports the results of an empirical study to evaluate the
impact of Dynamic Slicing (\ds{}) to improve \sfl{}. The intuition for
the \comb{} combination is that several highly ranked statements,
albeit covered by failing executions, may be unrelated to the
fault. Prior work reported promising results in this combination
\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012}.
For example, Lei \etal{}~\cite{lei-mao-dai-wang-2012} reported a
reduction of 78.3\% in \emph{effort}~\cite{7927959} to analyze
rankings when using dynamic slicing in combination with \sfl{} versus
plain \sfl{}. We found surprising that, despite these findings,
reported nearly 5 years ago, no tool or client analyses use this
combination today. One hypothesis to explain that observation is that
results reported in prior work are not as good as it seems. Prior
research evaluated \sfl{} using relative metrics, based on the
position of the first faulty statements found in the ranking relative
to the total number of ranking statements, which is often a very high
number. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact encouraging developers to adopt precise metrics
such as top@n
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. The
goal of this paper is to reassess whether the \comb{} combination is
worthwhile under the light of this metric. Developers of techniques
such as \acrAbrev{} would benefit from these results~---~either to
improve their results or to be aware they should not invest on this
integration.

@@

>>>>

%% Title information
\title{Reassessing the Impact of Dynamic Slicing in SFL}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
%\subtitle{Subtitle}                     %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% PROBLEM MOTIVATION
Software debugging is difficult. The task of locating the faulty code
(\ie{}, fault localization) is particularly challenging. For that
reason, countless automated techniques have been proposed in the past
to reduce cost of fault localization. Among those are Dynamic Slicing
(\ds{}) and Spectrum-Based Fault Localization (\sfl{}). Dynamic
Slicing~\cite{Agrawal:1990:DPS:93542.93576} takes as input a failing
test and produces on output a set of statements that influence the
evaluation of the fault-revealing assertion.  Although the technique
has been intensively explored, few slicing applications became
popular---WhyLine~\cite{Ko:2008:DRA:1368088.1368130} being an
exception.  \sfl{}~\cite{7390282} is another popular automated
debugging technique. It is a statistical fault localization method
that computes suspiciousness values associated with program entities
(e.g., basic blocks) using coverage information of passing and failing
test cases. \sfl{} produces a list of program entities ranked in
decreasing order of suspiciousness.  Likewise dynamic slicing, \sfl{}
received tremendous attention over the years, but its applicability to
support debugging remains
questionable~\cite{ang-perez-van-deursen-rui-2017,Pearson:2017:EIF:3097368.3097441,Xie:2016:RAD:2884781.2884834}.
Despite the skepticism of the research community, \sfl{} has been
shown useful in supporting downstream analyses, such as Automated
Program Repair
(\apr{})~\cite{automatic-software-repair-survey2017,kim-etal-daghstul2017},
an increasingly popular technique that looks for likely fixes to
likely buggy statements.  Tools like JAFF \cite{arcuri-2011}, Prophet
\cite{long-rinard-2016}, SemFix \cite{nguyen-qi-roychoudhury-2013},
and SPR \cite{long-rinard-2015} use \sfl{} to guide the search for
likely fixes.

@@

\ds{} and \sfl{} are complementary. Conceptually, \ds{} identifies
irrelevant parts of the code whereas \sfl{} ranks relevant parts of
the code.  This paper reports the results of an empirical study to
evaluate the impact of \ds{} to improve \sfl{}. The intuition for the
\comb{} combination is that several highly ranked statements, albeit
covered by failing executions, may be unrelated to the fault. Prior
work reported promising results in this combination
\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012}.
For example, Lei \etal{}~\cite{lei-mao-dai-wang-2012} reported a
reduction of 78.3\% in \emph{effort}~\cite{7927959} to analyze
rankings when using dynamic slicing in combination with \sfl{} versus
plain \sfl{}. We found surprising that, despite these findings,
reported nearly 5 years ago, no tool or client analyses use this
combination today. One hypothesis to explain that observation is that
results reported in prior work are not as good as it seems. Prior
research evaluated \sfl{} using relative metrics, based on the
position of the first faulty statements found in the ranking relative
to the total number of ranking statements, which is often a very high
number. Ang \etal~\cite{ang-perez-van-deursen-rui-2017} recently
pointed to that fact encouraging developers to adopt precise metrics
such as top@n
\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}. The
goal of this paper is to reassess whether the \comb{} combination is
worthwhile under the light of this metric and using a larger
dataset. Developers of \acrAbrev{} techniques would directly benefit
from these results~---~either to improve their results or to be aware
they should not invest on this integration.

@@

\subsection{Implementation}

\Mar{...elaborate...}
